Exploratory Plots

### 2020-05-28 exploratory/2020/README.Rmd
Don't need dist file for sub2

```{r fraction_reads_mapped}
df_fraction_mapped <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.txt'))
df_fraction_mapped %>% 
  ggplot(aes(dataset, fraction_mapped)) +
  geom_jitter()
```

>>>>

```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.txt'))
fractions %>% 
  ggplot(aes(dataset, fraction_mapped)) +
  geom_jitter()
```
